\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Chen Gang} % Your name
%\address{No.6 Kexueyuan South Road, District Haidian, Beijing, China} % Your secondary addess (optional)
\address{(+86)~18813188713 \\ cgangee@qq.com } % Your phone number and email

\begin{document}

\begin{rSection}{EDUCATION}
{\bf University of Chinese Academy of Sciences} \hfill {\em September 2015 - July 2018} \\
M.S. in Computer Applications Technology
\vspace{0.3em}

{\bf Zhengzhou University} \hfill {\em September 2011 - July 2015} \\
B.S. in Computer Science and Technology
\vspace{0.5em}
\end{rSection}



\begin{rSection}{Projects}

\begin{rSubsection}{Person and vehicle detection project}{Nov 2016 - Present}{}{}
\item Introduction: Detect bounding boxes of persons and vehicles in outdoor surveillance images, and predict detected persons' attributes and locations of body parts, meanwhile predict detected vehicles' types and brands. 
\item Responsibility: Develop person and vehicle detection module, which use deconvolution upscaling feature maps and online hard examples mining to optimize deep neural network PVANet, and improved every target detecting recall including person's head 21\% recall improvement while still remain 29 frames per second detecting speed.
\end{rSubsection}


\begin{rSubsection}{Tattoo identification project}{Oct 2016 - May 2017}{}{}
\item Introduction: Retrieve same tattoos took in different angles and lighting environment from the 100 thousand images database.
\item Responsibility: Clean and annotate tattoo images, with which train tattoo classification, detection and identification deep neural network.
Use the classification and detection network to remove images or images' area which don't include tattoo, and use identification network to extract features that used to retrieve tattoo images.
\end{rSubsection}

\begin{rSubsection}{Campus book sharing APP}{March 2015 - May 2015}{}{}
\item Introduction: An Android APP to post and gain information of books, and to chat with other users, which is implemented in Java and PHP.
\item Responsibility: responsible for software's overall design and development.
\end{rSubsection}


\end{rSection}



\begin{rSection}{HONORS}
\begin{list}{$\cdot$}{\leftmargin=0em}
\itemsep -0.2em \vspace{0em}
\item First Prize, The $5^{th}$ Blue Bridge Cup National Software Contest Finals, First Prize \hfill {2014}
\item 2 Bronze Medals, The $38^{th}$ ACM-ICPC Asia Regionals \hfill {2013}
\item First place 3 times, The $5^{th}$ - $7^{th}$ ACM Henan Provincial Programming Contest \hfill {2012-2014}
\item National Encouragement Scholarship \hfill {2013}
%\item Scholarship for Outstanding Students, Second Prize \hfill {2014}
\end{list}
\vspace{0.5em}
\end{rSection}


\begin{rSection}{Experience}
\begin{rSubsection}{Baidu Map}{March 2015 - May 2015}{RD Intern}{Beijing}
\item Optimized 2.5 million navigation coordinates of points of interest (POI) of 80 million POI in Baidu Map, about 3\%.
\item Generated users driving and navigation paths according navigation GPS log files, which used to compute and analyze yaw points.
\end{rSubsection}
\end{rSection}


\begin{rSection}{Technical Strengths}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & C/C++, Python, Java, Shell\\
Tools & Caffe, Git, Vim \\
English & CET-4, CET-6 \\
\end{tabular}
\end{rSection}




\end{document}
