\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Chen Gang} % Your name
\address{Yanqi Lake \\ District Huairou \\ Beijing 101408 CHINA} % Your secondary addess (optional)
\address{(+86)~188-1318-8713 \\ cgangee@gmail.com \\ www.cgangee.com} % Your phone number and email

\begin{document}



\begin{rSection}{EDUCATION}
{\bf University of Chinese Academy of Sciences} \hfill {\em September 2015 - July 2018} \\
M.S. in Computer Application Technology
\vspace{0.3em}

{\bf Zhengzhou University} \hfill {\em September 2011 - July 2015} \\
B.S. in Computer Science \& Technology
\vspace{0.5em}
\end{rSection}




\begin{rSection}{Experience}
\begin{rSubsection}{Baidu Map}{March 2015 - May 2015}{RD Intern}{Beijing, China}
\item Optimized 2.5 million navigation coordinates of points of interest (POI) of 80 million POI in Baidu Map.
\item Yaw points statistics and analysis from 12TB navigation log files. Discovered yaw points obey long tail distribution.
\end{rSubsection}
\end{rSection}






\begin{rSection}{Technical Strengths}
\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & C/C++, Java, Shell, PHP, \LaTeX, JavaScript \\
Tools & Git, Vim \\
English & CET-4, CET-6 \\
Others & Algorithm Design, Machine Learning, Computer Vision
\end{tabular}
\end{rSection}



\begin{rSection}{Projects}
\begin{rSubsection}{fzrOJ}{July 2013 - September 2013}{}{}
\item An online system to test programs in programming contest is implemented in C++ and PHP, which can compile and execute submitted code, and test them with pre-constructed data.
\item Responsibility: full stack developer. 
\item Currently working at http://acm.zzu.edu.cn/fzrOJ.
\end{rSubsection}

\begin{rSubsection}{Campus Sharing Book APP}{March 2015 - May 2015}{}{}
\item An Android APP to post and gain information of books, and to chat with other users, which is implemented in Java and PHP.
\item Crawled users' information from website of school.
\item Responsibility: full stack developer.
\end{rSubsection}
\end{rSection}




\begin{rSection}{HONORS}
\begin{list}{$\cdot$}{\leftmargin=0em}
\itemsep -0.2em \vspace{0em}
\item The $5^{th}$ - $7^{th}$ ACM-ICPC Henan Provincial Programming Contest, 3 Gold Medals \hfill {2012-2014}
\item The $38^{th}$ ACM-ICPC Asia Regionals, 2 Bronze Medals\hfill {2013}
\item The $5^{th}$ Blue Bridge Cup National Software Contest Finals, First Prize \hfill {2014}
\item National Encouragement Scholarship \hfill {2013}
\item Scholarship for Outstanding Students, Second Prize \hfill {2014}
\end{list}
\vspace{0.5em}
\end{rSection}





\end{document}
